### 2019-02-19 sections/intuition.tex
intuition: collaboration patterns

\subsection{Tasks model real world collaborations between people and machines}

The central objective of \TOP is to \emph{coordinate collaboration}.
The basic building blocks of \TOPHAT are editors and combinators.
Editors are tasks with which users interact directly.
Combinators express ways in which people can work together.
Tasks can be executed after each other, at the same time, or conditionally.
This motivates the combinators step ($\Then$, $\Next$), parallel ($\And$), and choice ($\Or$, $\Xor$).

@@

The following program shows the different collaboration operators in action.
Users have a choice whether they want tea or coffee.
They always get an egg.
The drink and the food are prepared in parallel.
When drink and food are prepared, users can step to eating the result.

>>>>

The central objective of \TOP is to \emph{coordinate collaboration}.
The basic building blocks of \TOPHAT for this are task combinators.
They express ways in which people can work together.
Tasks can be executed after each other, at the same time, or conditionally.
This motivates the combinators step ($\Then$, $\Next$), parallel ($\And$), and choice ($\Or$, $\Xor$).

@@

The following program shows the different collaboration operators in action.
Users have a choice ($\Xor$) whether they want tea or coffee.
They always get an egg.
The drink and the food are prepared in parallel ($\And$).
When drink and food are prepared, users can step ($\Next$) to eating the results.
